---
title: "TB CAPT costing Mozambique 1.5x"
author: "Akash Malhotra"
date: "1/15/2024"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Research Questions: 

1. What is the mean difference in household and health system costs/benefits per participant tested and per TB patient identified for delivering TB testing between the intervention and the control arms? 

2. What is the incremental cost-effectiveness ratio (ICER) between the control and intervention arms where effectiveness is modeled as the number of TB patients identified within one week of initial care seeking?   

Intervention Arm: xx participants tested via Molbio Truenat for 5 months in the intervention arm
Control SoC arm: yy participants tested via GeneXpert for 5 months in the standard of care arm 

Inputs


Truenat arm:

-- initiated on TB treatment within a week as a proportion of all tested
-- delivery costs per participant tested
-- household costs per participant tested

SOC arm : 

-- initiated on TB treatment within a week as a proportion of all tested
-- delivery costs per participant tested
-- household costs per participant tested

```{r packages}
library (tidyverse)
library(ggplot2)
library(dplyr)
library(triangle)
library(car)
library(collapse)

params <- read.csv("parameters_moz.csv")

lambda <- 0.7 #change back to 0.7 for base case
#lambda_row <- 4
lambda_values <- c(0.1, 0.2, 0.5, 0.7, 1, 2, 3, 4, 6, 8, 12, 16)
lambda_row <- which(lambda_values == lambda)


params <- params[lambda_row,]

params_row <- params


```

#First, set up the treatment.sim function by denoting all relevant input parameters you’re doing PSA with, and then some function for coming up with your total costs and total effectiveness. (may just be an aggregate sum of each).

```{r create model parameters}

#UPDATE ALL #cluster ratio vs overall ratio?
treatment.sim<-function(
    num.test.int, #number of participants tested in the intervention arm 
    num.test.con, #number of participants tested in the control arm
    ratio.oc.int, #proportion of participants having the primary outcome in intervention arm
    ratio.oc.con, #proportion of participants having the primary outcome in control arm
    ratio.ltc.int, #proportion of participants linked to care over the year in the intervention arm  
    ratio.ltc.con, # proportion of particpants linked to care over the year in the control arm 
    cost.test.int, #cartridge costs in intervention arm 
    cost.cons.int, #other consumables in the intervention arm
    cost.eqp.int, #equipment cost in intervention arm 
    cost.war.int, #warranty and maint cost intervention arm 
    cost.trn.int, #training costs in the intervention arm 
    cost.cme.int, #comm and M&E costs intervention arm 
    cost.hss.int, #health system staff costs in the intervention arm 
    cost.misc.int, # misc costs in the intervention arm 
    cost.fee.int, # intervention fee
    cost.lab.int, # intervention lab
    cost.med.int, # intervention medicine
    cost.trv.int, # travel 
    cost.food.int, #including food for person accompanying
    cost.chc.int,#including childcare for person accompanying
    cost.mw.int, # itnervention missed work
    cost.oth.int, # itnervention other
    cost.test.con, #cartridge costs in control arm  
    cost.cons.con, #other consumables in the control arm 
    cost.eqp.con, #equipment cost in the control arm 
    cost.war.con, #warranty and maint cost control arm 
    cost.trn.con, #training costs in the control arm 
    cost.cme.con, #comm and M&E costs control arm
    cost.hss.con, #health system staff costs in the intervention arm 
    cost.misc.con, # misc costs in the control arm 
    cost.fee.con, # control fee
    cost.lab.con, # control lab
    cost.med.con, # control medicine
    cost.trv.con, # travel control
    cost.food.con,#including food for person accompanying
    cost.chc.con,#including childcare for person accompanying
    cost.mw.con,  # control missed work
    cost.oth.con # control other
)
    
    #cost.err.int, #per household error costs in the intervention arm +- 10%
    #cost.err.con, #per household error costs in the control arm +- 10% 
    
      { #Here, set up our values of interest (total cost and # of patients initiating and completing treatment)
 
  tot.oc.int <- ratio.oc.int*num.test.int # no. of people with outcome, denominator for CE
  tot.oc.con <- ratio.oc.con*num.test.con
  
  tot.ltc.int <- ratio.ltc.int*num.test.int # no. of people linked to care over the year
  tot.ltc.con <- ratio.ltc.con*num.test.con
  
  cost.tot.int <- cost.test.int + cost.cons.int + cost.eqp.int + cost.war.int + cost.trn.int + cost.cme.int + cost.hss.int + cost.misc.int
  
  cost.pat.int <- cost.fee.int + cost.lab.int + cost.med.int + cost.trv.int + cost.food.int + cost.chc.int + cost.mw.int + cost.oth.int
  
  
  cost.soc.int <- cost.tot.int + cost.pat.int 
  ovr.cost.int <- num.test.int*cost.soc.int #numerator for CE
  
  cost.tot.con <- cost.test.con + cost.cons.con + cost.eqp.con + cost.war.con + cost.trn.con + cost.cme.con + cost.hss.con + cost.misc.con
  
   cost.pat.con <- cost.fee.con + cost.lab.con + cost.med.con + 1.5*cost.trv.con + 1.5*cost.food.con + 1.5*cost.chc.con + 1.5*cost.mw.con + 1.5*cost.oth.con
  
  cost.soc.con <- cost.tot.con + cost.pat.con 
   ovr.cost.con <- num.test.con*cost.soc.con #numerator for CE
 
 ########### ICER VALUES #############
  incr.total.cost <- (ovr.cost.int - ovr.cost.con)
  incr.total.effect <- (tot.oc.int - tot.oc.con)
  
  incr.ratio <- (incr.total.cost / incr.total.effect) #primary CE outcome
  
  cost.per.oc.int <- ovr.cost.int/tot.oc.int #primary cost outcome
  cost.per.oc.con <- ovr.cost.con/tot.oc.con
  

  
  #return the key results: cure and cost in each scenario
    

  results<-c(num.test.int,
             num.test.con,
             ratio.oc.int,
             ratio.oc.con,
             ratio.ltc.int,
             ratio.ltc.con,
             tot.oc.int,
             tot.oc.con,
             tot.ltc.int,
             tot.ltc.con,
             cost.test.int,
             cost.cons.int,
             cost.eqp.int,
             cost.war.int,
             cost.trn.int,
             cost.cme.int,
             cost.hss.int,
             cost.misc.int,
             cost.tot.int,
             cost.fee.int,
             cost.lab.int,
             cost.med.int,
             cost.trv.int,
             cost.food.int,
             cost.chc.int,
             cost.mw.int,
             cost.oth.int,
             cost.pat.int,
             cost.soc.int,
             ovr.cost.int,
             cost.test.con,
             cost.cons.con,
             cost.eqp.con,
             cost.war.con,
             cost.trn.con,
             cost.cme.con,
             cost.hss.con,
             cost.misc.con,
             cost.tot.con,
             cost.fee.con,
             cost.lab.con,
             cost.med.con,
             cost.trv.con,
             cost.food.con,
             cost.chc.con,
             cost.mw.con,
             cost.oth.con,
             cost.pat.con,
             cost.soc.con,
             ovr.cost.con
             )
  
   names(results)<-c("Number of tests intervention",
                     "Number of tests control",
                     "Outcome ratio intervention",
                     "Outcome ratio control",
                     "linkage to care ratio intervention",
                     "linkage to care ratio control",
                     "Total outcomes intervention",
                     "Total outcomes control",
                     "Total linkage to care intervention",
                     "Total linkage to care control",
                    "cartridge costs intervention",
                    "Other consumables costs intervention",
                    "equipment cost intervention",
                    "warranty and maintenance costs intervention",
                    "training costs intervention",
                     "communication and M&E costs intervention",
                    "Health system staffing costs intervention",
                    "miscellaneous costs intervention",
                    "total costs intervention", 
                    "testing fee intervention",
                    "lab cost intervention",
                    "medicine cost intervention",
                    "travel cost intervention",
                    "food cost intervention",
                    "childcare cost intervention",
                    "missed work cost intervention",
                    "other cost intervention",
                    "total patient cost intervention",
                    "total societal cost intervention",
                    "Overall cost intrvention",
                    "cartridge costs control",
                    "Other consumables costs control",
                    "equipment cost control",
                    "warranty and maintenance costs control",
                    "training costs control",
                    "communication and M&E costs control",
                    "Health system staffing costs control",
                    "miscellaneous costs control",
                    "total costs control",
                      "testing fee control",
                    "lab cost control",
                    "medicine cost control",
                    "travel cost control",
                    "food cost control",
                    "childcare cost control",
                    "missed work cost control",
                    "other cost control",
                    "total patient cost control",
                    "total societal cost control",
                    "overall cost control"
   )
           
  
  return(results)
}
```       


```{r set-up the parameter values}
param.ranges<-data.frame("variable"=character(38), 
                         "distribution"=character(38),
                         "parameter1"=numeric(38),
                         "parameter2"=numeric(38),
                         "parameter3"=numeric(38),
                         "parameter1.name"=numeric(38), 
                         "parameter2.name"=numeric(38),
                         "parameter3.name"=numeric(38))

param.ranges[,"variable"]<-c(
             "num.test.int",
             "num.test.con",
             "ratio.oc.int",
             "ratio.oc.con",
             "ratio.ltc.int",
             "ratio.ltc.con",
             "cost.test.int",
             "cost.cons.int",
             "cost.eqp.int",
             "cost.war.int",
             "cost.trn.int",
             "cost.cme.int",
             "cost.hss.int",
             "cost.misc.int",
             "cost.fee.int",
             "cost.lab.int",
             "cost.med.int",
             "cost.trv.int",
             "cost.food.int",
             "cost.chc.int",
             "cost.mw.int",
             "cost.oth.int",
             "cost.test.con",
             "cost.cons.con",
             "cost.eqp.con",
             "cost.war.con",
             "cost.trn.con",
             "cost.cme.con",
             "cost.hss.con",
             "cost.misc.con",
             "cost.fee.con",
             "cost.lab.con",
             "cost.med.con",
             "cost.trv.con",
             "cost.food.con",
             "cost.chc.con",
             "cost.mw.con",
             "cost.oth.con"
             
            )

#Assigns a name to each of the above variables in the param.ranges data frame.

           
param.ranges[,"distribution"]<-c(
"beta", #Tested in intervention arm
"beta", #Tested in control arm
"beta", #outcome ratio intervention arm
"beta", #outcome ratio control arm
"beta", #linkage to care intervention
"beta", #linkage to care control
"beta", #Intervention cartridge costs
"beta", #intervention other consumables costs
"beta", #intervention equipment costs
"beta", #intervention warranty and maintenance costs
"beta", #intervention training costs
"beta", #intervention communication and M&E costs
"beta", #intervention staffing costs
"beta", #intervention misc costs
"beta", #intervention fee
"beta", #intervention lab
"beta", #intervention med
"beta", # intervention travel
"beta", # intervention food
"beta", #intervention childcare
"beta", #intervention missed work
"beta", #intervention other
"beta", #control cartridge costs
"beta", #control other consumables costs
"beta", #control equipment costs
"beta", #control warranty and maintenance costs
"beta", #control training costs
"beta", #control communication and M&E costs
"beta", #control staffing costs
"beta", #control misc costs
"beta", # control fee
"beta", # control lab
"beta", # control med
"beta", # control travel
"beta", # control food
"beta", # control childcare
"beta", # control missed work
"beta" # control other
)
#Assigns a distribution to each parameter. Note: common cost distributions are uniform, normal, triangular, and beta.

# numbers fed in based on lamda = 0.7 and avg tests per month in both arms

#Minimum values
 param.ranges[,"parameter1"]<-c(
    params_row$min.num.test.int, #number of participants tested in the intervention arm 
    params_row$min.num.test.con, #number of participants tested in the control arm
    params_row$min.ratio.oc.int, #proportion of participants having the primary outcome in intervention arm
    params_row$min.ratio.oc.con, #proportion of participants having the primary outcome in control arm
    params_row$min.ratio.ltc.int, #proportion of participants linked to care over 60 days in intervention
    params_row$min.ratio.ltc.con, # proportion of particpants linked to care over the year in the control arm 
    params_row$min.cost.test.int, #cartridge costs in intervention arm 
    params_row$min.cost.cons.int, #other consumables in the intervention arm
    params_row$min.cost.eqp.int, #equipment cost in intervention arm 
    params_row$min.cost.war.int, #warranty and maint cost intervention arm 
    params_row$min.cost.trn.int, #training costs in the intervention arm 
    params_row$min.cost.cme.int, #comm and M&E costs intervention arm 
    params_row$min.cost.hss.int, #health system staff costs in the intervention arm 
    params_row$min.cost.misc.int, # misc costs in the intervention arm 
    params_row$min.cost.fee.int, # intervention fee
    params_row$min.cost.lab.int, # intervention lab
    params_row$min.cost.med.int, # intervention medicine
    params_row$min.cost.trv.int, # travel 
    params_row$min.cost.food.int, #including food for person accompanying
    params_row$min.cost.chc.int,#including childcare for person accompanying
    params_row$min.cost.mw.int, # itnervention missed work
    params_row$min.cost.oth.int, # itnervention other
    params_row$min.cost.test.con, #cartridge costs in control arm  
    params_row$min.cost.cons.con, #other consumables in the control arm 
    params_row$min.cost.eqp.con, #equipment cost in the control arm 
    params_row$min.cost.war.con, #warranty and maint cost control arm 
    params_row$min.cost.trn.con, #training costs in the control arm 
    params_row$min.cost.cme.con, #comm and M&E costs control arm
    params_row$min.cost.hss.con, #health system staff costs in the intervention arm 
    params_row$min.cost.misc.con, # misc costs in the control arm 
    params_row$min.cost.fee.con, # control fee
    params_row$min.cost.lab.con, # control lab
    params_row$min.cost.med.con, # control medicine
    params_row$min.cost.trv.con, # travel control
    params_row$min.cost.food.con,#including food for person accompanying
    params_row$min.cost.chc.con,#including childcare for person accompanying
    params_row$min.cost.mw.con,  # control missed work
    params_row$min.cost.oth.con # control other
)

 #Max values
  param.ranges[,"parameter2"]<-c(
    params_row$max.num.test.int, #number of participants tested in the intervention arm 
    params_row$max.num.test.con, #number of participants tested in the control arm
    params_row$max.ratio.oc.int, #proportion of participants having the primary outcome in intervention arm
    params_row$max.ratio.oc.con, #proportion of participants having the primary outcome in control arm
    params_row$max.ratio.ltc.int, #proportion of participants linked to care over the year in the intervention
    params_row$max.ratio.ltc.con, # proportion of particpants linked to care over the year in the control arm 
    params_row$max.cost.test.int, #cartridge costs in intervention arm 
    params_row$max.cost.cons.int, #other consumables in the intervention arm
    params_row$max.cost.eqp.int, #equipment cost in intervention arm 
    params_row$max.cost.war.int, #warranty and maint cost intervention arm 
    params_row$max.cost.trn.int, #training costs in the intervention arm 
    params_row$max.cost.cme.int, #comm and M&E costs intervention arm 
    params_row$max.cost.hss.int, #health system staff costs in the intervention arm 
    params_row$max.cost.misc.int, # misc costs in the intervention arm 
    params_row$max.cost.fee.int, # intervention fee
    params_row$max.cost.lab.int, # intervention lab
    params_row$max.cost.med.int, # intervention medicine
    params_row$max.cost.trv.int, # travel 
    params_row$max.cost.food.int, #including food for person accompanying
    params_row$max.cost.chc.int,#including childcare for person accompanying
    params_row$max.cost.mw.int, # itnervention missed work
    params_row$max.cost.oth.int, # itnervention other
    params_row$max.cost.test.con, #cartridge costs in control arm  
    params_row$max.cost.cons.con, #other consumables in the control arm 
    params_row$max.cost.eqp.con, #equipment cost in the control arm 
    params_row$max.cost.war.con, #warranty and maint cost control arm 
    params_row$max.cost.trn.con, #training costs in the control arm 
    params_row$max.cost.cme.con, #comm and M&E costs control arm
    params_row$max.cost.hss.con, #health system staff costs in the intervention arm 
    params_row$max.cost.misc.con, # misc costs in the control arm 
    params_row$max.cost.fee.con, # control fee
    params_row$max.cost.lab.con, # control lab
    params_row$max.cost.med.con, # control medicine
    params_row$max.cost.trv.con, # travel control
    params_row$max.cost.food.con,#including food for person accompanying
    params_row$max.cost.chc.con,#including childcare for person accompanying
    params_row$max.cost.mw.con,  # control missed work
    params_row$max.cost.oth.con # control other
)
  #PE
    param.ranges[,"parameter3"]<-c(
    params_row$pe.num.test.int, #number of participants tested in the intervention arm 
    params_row$pe.num.test.con, #number of participants tested in the control arm
    params_row$pe.ratio.oc.int, #proportion of participants having the primary outcome in intervention arm
    params_row$pe.ratio.oc.con, #proportion of participants having the primary outcome in control arm
    params_row$pe.ratio.ltc.int, #proportion of participants linked to care over the year in the intervention
    params_row$pe.ratio.ltc.con, # proportion of particpants linked to care over the year in the control arm 
    params_row$pe.cost.test.int, #cartridge costs in intervention arm 
    params_row$pe.cost.cons.int, #other consumables in the intervention arm
    params_row$pe.cost.eqp.int, #equipment cost in intervention arm 
    params_row$pe.cost.war.int, #warranty and maint cost intervention arm 
    params_row$pe.cost.trn.int, #training costs in the intervention arm 
    params_row$pe.cost.cme.int, #comm and M&E costs intervention arm 
    params_row$pe.cost.hss.int, #health system staff costs in the intervention arm 
    params_row$pe.cost.misc.int, # misc costs in the intervention arm 
    params_row$pe.cost.fee.int, # intervention fee
    params_row$pe.cost.lab.int, # intervention lab
    params_row$pe.cost.med.int, # intervention medicine
    params_row$pe.cost.trv.int, # travel 
    params_row$pe.cost.food.int, #including food for person accompanying
    params_row$pe.cost.chc.int,#including childcare for person accompanying
    params_row$pe.cost.mw.int, # itnervention missed work
    params_row$pe.cost.oth.int, # itnervention other
    params_row$pe.cost.test.con, #cartridge costs in control arm  
    params_row$pe.cost.cons.con, #other consumables in the control arm 
    params_row$pe.cost.eqp.con, #equipment cost in the control arm 
    params_row$pe.cost.war.con, #warranty and maint cost control arm 
    params_row$pe.cost.trn.con, #training costs in the control arm 
    params_row$pe.cost.cme.con, #comm and M&E costs control arm
    params_row$pe.cost.hss.con, #health system staff costs in the intervention arm 
    params_row$pe.cost.misc.con, # misc costs in the control arm 
    params_row$pe.cost.fee.con, # control fee
    params_row$pe.cost.lab.con, # control lab
    params_row$pe.cost.med.con, # control medicine
    params_row$pe.cost.trv.con, # travel control
    params_row$pe.cost.food.con,#including food for person accompanying
    params_row$pe.cost.chc.con,#including childcare for person accompanying
    params_row$pe.cost.mw.con,  # control missed work
    params_row$pe.cost.oth.con # control other
)
    ```
    
```{r add the alpha and beta values}
#Updated with inflation
param.ranges[,"parameter1.name"]<-c( #The ALPHA value
    params_row$alpha.num.test.int, #number of participants tested in the intervention arm 
    params_row$alpha.num.test.con, #number of participants tested in the control arm
    params_row$alpha.ratio.oc.int, #proportion of participants having the primary outcome in intervention arm
    params_row$alpha.ratio.oc.con, #proportion of participants having the primary outcome in control arm
    params_row$alpha.ratio.ltc.int, #proportion of participants linked to care over the year in the intervent
    params_row$alpha.ratio.ltc.con, # proportion of particpants linked to care over the year in the control 
    params_row$alpha.cost.test.int, #cartridge costs in intervention arm 
    params_row$alpha.cost.cons.int, #other consumables in the intervention arm
    params_row$alpha.cost.eqp.int, #equipment cost in intervention arm 
    params_row$alpha.cost.war.int, #warranty and maint cost intervention arm 
    params_row$alpha.cost.trn.int, #training costs in the intervention arm 
    params_row$alpha.cost.cme.int, #comm and M&E costs intervention arm 
    params_row$alpha.cost.hss.int, #health system staff costs in the intervention arm 
    params_row$alpha.cost.misc.int, # misc costs in the intervention arm 
    params_row$alpha.cost.fee.int, # intervention fee
    params_row$alpha.cost.lab.int, # intervention lab
    params_row$alpha.cost.med.int, # intervention medicine
    params_row$alpha.cost.trv.int, # travel 
    params_row$alpha.cost.food.int, #including food for person accompanying
    params_row$alpha.cost.chc.int,#including childcare for person accompanying
    params_row$alpha.cost.mw.int, # itnervention missed work
    params_row$alpha.cost.oth.int, # itnervention other
    params_row$alpha.cost.test.con, #cartridge costs in control arm  
    params_row$alpha.cost.cons.con, #other consumables in the control arm 
    params_row$alpha.cost.eqp.con, #equipment cost in the control arm 
    params_row$alpha.cost.war.con, #warranty and maint cost control arm 
    params_row$alpha.cost.trn.con, #training costs in the control arm 
    params_row$alpha.cost.cme.con, #comm and M&E costs control arm
    params_row$alpha.cost.hss.con, #health system staff costs in the intervention arm 
    params_row$alpha.cost.misc.con, # misc costs in the control arm 
    params_row$alpha.cost.fee.con, # control fee
    params_row$alpha.cost.lab.con, # control lab
    params_row$alpha.cost.med.con, # control medicine
    params_row$alpha.cost.trv.con, # travel control
    params_row$alpha.cost.food.con,#including food for person accompanying
    params_row$alpha.cost.chc.con,#including childcare for person accompanying
    params_row$alpha.cost.mw.con,  # control missed work
    params_row$alpha.cost.oth.con # control other
  )
  
param.ranges[,"parameter2.name"]<-c( #The BETA value
    params_row$beta.num.test.int, #number of participants tested in the intervention arm 
    params_row$beta.num.test.con, #number of participants tested in the control arm
    params_row$beta.ratio.oc.int, #proportion of participants having the primary outcome in intervention arm
    params_row$beta.ratio.oc.con, #proportion of participants having the primary outcome in control arm
    params_row$beta.ratio.ltc.int, #proportion of participants linked to care over the year in the interve
    params_row$beta.ratio.ltc.con, # proportion of particpants linked to care over the year in the control a
    params_row$beta.cost.test.int, #cartridge costs in intervention arm 
    params_row$beta.cost.cons.int, #other consumables in the intervention arm
    params_row$beta.cost.eqp.int, #equipment cost in intervention arm 
    params_row$beta.cost.war.int, #warranty and maint cost intervention arm 
    params_row$beta.cost.trn.int, #training costs in the intervention arm 
    params_row$beta.cost.cme.int, #comm and M&E costs intervention arm 
    params_row$beta.cost.hss.int, #health system staff costs in the intervention arm 
    params_row$beta.cost.misc.int, # misc costs in the intervention arm 
    params_row$beta.cost.fee.int, # intervention fee
    params_row$beta.cost.lab.int, # intervention lab
    params_row$beta.cost.med.int, # intervention medicine
    params_row$beta.cost.trv.int, # travel 
    params_row$beta.cost.food.int, #including food for person accompanying
    params_row$beta.cost.chc.int,#including childcare for person accompanying
    params_row$beta.cost.mw.int, # itnervention missed work
    params_row$beta.cost.oth.int, # itnervention other
    params_row$beta.cost.test.con, #cartridge costs in control arm  
    params_row$beta.cost.cons.con, #other consumables in the control arm 
    params_row$beta.cost.eqp.con, #equipment cost in the control arm 
    params_row$beta.cost.war.con, #warranty and maint cost control arm 
    params_row$beta.cost.trn.con, #training costs in the control arm 
    params_row$beta.cost.cme.con, #comm and M&E costs control arm
    params_row$beta.cost.hss.con, #health system staff costs in the intervention arm 
    params_row$beta.cost.misc.con, # misc costs in the control arm 
    params_row$beta.cost.fee.con, # control fee
    params_row$beta.cost.lab.con, # control lab
    params_row$beta.cost.med.con, # control medicine
    params_row$beta.cost.trv.con, # travel control
    params_row$beta.cost.food.con,#including food for person accompanying
    params_row$beta.cost.chc.con,#including childcare for person accompanying
    params_row$beta.cost.mw.con,  # control missed work
    params_row$beta.cost.oth.con # control other
  )

param.ranges[,"parameter3.name"]<-c(#Non-centrality parameter,
    params_row$ncp.num.test.int, #number of participants tested in the intervention arm 
    params_row$ncp.num.test.con, #number of participants tested in the control arm
    params_row$ncp.ratio.oc.int, #proportion of participants having the primary outcome in intervention arm
    params_row$ncp.ratio.oc.con, #proportion of participants having the primary outcome in control arm
    params_row$ncp.ratio.ltc.int, #proportion of participants linked to care over the year in the interve
    params_row$ncp.ratio.ltc.con, # proportion of particpants linked to care over the year in the control a
    params_row$ncp.cost.test.int, #cartridge costs in intervention arm 
    params_row$ncp.cost.cons.int, #other consumables in the intervention arm
    params_row$ncp.cost.eqp.int, #equipment cost in intervention arm 
    params_row$ncp.cost.war.int, #warranty and maint cost intervention arm 
    params_row$ncp.cost.trn.int, #training costs in the intervention arm 
    params_row$ncp.cost.cme.int, #comm and M&E costs intervention arm 
    params_row$ncp.cost.hss.int, #health system staff costs in the intervention arm 
    params_row$ncp.cost.misc.int, # misc costs in the intervention arm 
    params_row$ncp.cost.fee.int, # intervention fee
    params_row$ncp.cost.lab.int, # intervention lab
    params_row$ncp.cost.med.int, # intervention medicine
    params_row$ncp.cost.trv.int, # travel 
    params_row$ncp.cost.food.int, #including food for person accompanying
    params_row$ncp.cost.chc.int,#including childcare for person accompanying
    params_row$ncp.cost.mw.int, # itnervention missed work
    params_row$ncp.cost.oth.int, # itnervention other
    params_row$ncp.cost.test.con, #cartridge costs in control arm  
    params_row$ncp.cost.cons.con, #other consumables in the control arm 
    params_row$ncp.cost.eqp.con, #equipment cost in the control arm 
    params_row$ncp.cost.war.con, #warranty and maint cost control arm 
    params_row$ncp.cost.trn.con, #training costs in the control arm 
    params_row$ncp.cost.cme.con, #comm and M&E costs control arm
    params_row$ncp.cost.hss.con, #health system staff costs in the intervention arm 
    params_row$ncp.cost.misc.con, # misc costs in the control arm 
    params_row$ncp.cost.fee.con, # control fee
    params_row$ncp.cost.lab.con, # control lab
    params_row$ncp.cost.med.con, # control medicine
    params_row$ncp.cost.trv.con, # travel control
    params_row$ncp.cost.food.con,#including food for person accompanying
    params_row$ncp.cost.chc.con,#including childcare for person accompanying
    params_row$ncp.cost.mw.con,  # control missed work
    params_row$ncp.cost.oth.con # control other
  ) 


```

```{r simulation prep, repetitions and matrix}
#Define the number of simulations you intend to perform
set.seed(26910)
n.sims<-10000


#Create a matrix to hold all of the sampled parameter values
#Each row will represent 1 simulation; the columns in the row will correspond to the sampled parameter values for the row
sampled.values<-matrix(nrow=n.sims,ncol=nrow(param.ranges))
colnames(sampled.values)<-param.ranges[,"variable"]

#Loop over the parameters (columns in sampled.values, rows in param.ranges) that will be sampled
for(p in 1:ncol(sampled.values)){
  
  #check for the distribution that will be used
  #check for a uniform distribution
  if(param.ranges[p,"distribution"]=="uniform"){
    
    n.params<-runif( #sample from a uniform distribution
      n.sims, #how many samples to draw = the number of simulations you will perform
      min=param.ranges[p,"parameter1"], #define the lower bound parameter
      max=param.ranges[p,"parameter2"] #define the upper bound
    )
    #exit the if-loop and go to the end
    
  }
  #if not uniform, check if it is normal
  if(param.ranges[p,"distribution"]=="normal"){
    
    n.params<-rnorm( #sample from a normal distribution
      n.sims, #how many samples to draw = the number of simulations you will perform
      mean=param.ranges[p,"parameter1"], #define the lower bound parameter
      sd=param.ranges[p,"parameter2"] #define the upper bound
    )
    #exit the if-loop and go to the end
    
  }
  
  #if not uniform, check if it is lognormal
  if(param.ranges[p,"distribution"]=="lognormal"){
    
    n.params<-rlnorm( #sample from a log-normal distribution
      n.sims, #how many samples to draw = the number of simulations you will perform
      meanlog=param.ranges[p,"parameter1"], #define the mean parameter
      sdlog=param.ranges[p,"parameter2"] #define the standard deviation parameter
    )
    #exit the if-loop and go to the end
    
  }
  
  #if not lognormal, check if it is gamma
  if(param.ranges[p,"distribution"]=="gamma"){
    n.params<-rgamma( #sample from a log-normal distribution
      n.sims, #how many samples to draw = the number of simulations you will perform
      shape=param.ranges[p,"parameter1"], #define the k parameter
      scale=param.ranges[p,"parameter2"] #define the theta parameter
    )
    #exit the if-loop and go to the end
    
  }
  
  #if not gamma, check if it is triangular
  if(param.ranges[p,"distribution"]=="triangular"){
    n.params<- rtriangle( #sample from a triangular distribution
      n.sims, #how many samples to draw = the number of simulations you will perform
      a = param.ranges[p,"parameter1"], #define the lower bound paramater/parameter input 1
      b = param.ranges[p,"parameter2"], #define the upper bound parameter
      c = param.ranges[p,"parameter3"] #define the mode/central tendency parameter
    )
  }
  
  #if not triangular, check if it is beta
 if(param.ranges[p,"distribution"]=="beta"){
    shape1 <- as.numeric(param.ranges[p,"parameter1.name"])
    shape2 <- as.numeric(param.ranges[p,"parameter2.name"])
    
    if(!is.numeric(shape1) || !is.numeric(shape2)) {
        stop("Shape parameters for beta distribution must be numeric.")
    }
    
    n.params <- rbeta(
      n.sims, 
      shape1 = shape1, 
      shape2 = shape2,
      ncp = param.ranges[p,"parameter3.name"] #define the non-centrality parameter (should be 0)
    ) 
    #(parameter1 + (p *(parameter2 - parameter1)))
  }
  sampled.values[,p]<-n.params #fill the column of the matrix with the vector of sampled values
  
  #go to the next column
}

```

```{r calculate "true" simulated values}
#Change variable names to match TB CAPT, no other changes


num.test.int <- (sampled.values[,1] * (as.numeric(param.ranges[1,4]) - as.numeric(param.ranges[1,3]))) + as.numeric(param.ranges[1,3])

num.test.con <- (sampled.values[,2] * (as.numeric(param.ranges[2,4]) - as.numeric(param.ranges[2,3]))) + as.numeric(param.ranges[2,3])

ratio.oc.int <- (sampled.values[,3] * (as.numeric(param.ranges[3,4]) - as.numeric(param.ranges[3,3]))) + as.numeric(param.ranges[3,3])

ratio.oc.con <- (sampled.values[,4] * (as.numeric(param.ranges[4,4]) - as.numeric(param.ranges[4,3]))) + as.numeric(param.ranges[4,3])

ratio.ltc.int <- (sampled.values[,5] * (as.numeric(param.ranges[5,4]) - as.numeric(param.ranges[5,3]))) + as.numeric(param.ranges[5,3])

ratio.ltc.con <- (sampled.values[,6] * (as.numeric(param.ranges[6,4]) - as.numeric(param.ranges[6,3]))) + as.numeric(param.ranges[6,3])

cost.test.int <- (sampled.values[,7] * (as.numeric(param.ranges[7,4]) - as.numeric(param.ranges[7,3]))) + as.numeric(param.ranges[7,3])

cost.cons.int <- (sampled.values[,8] * (as.numeric(param.ranges[8,4]) - as.numeric(param.ranges[8,3]))) + as.numeric(param.ranges[8,3]) 

cost.eqp.int<- (sampled.values[,9] * (as.numeric(param.ranges[9,4]) - as.numeric(param.ranges[9,3]))) + as.numeric(param.ranges[9,3])

cost.war.int <- (sampled.values[,10] * (as.numeric(param.ranges[10,4]) - as.numeric(param.ranges[10,3]))) + as.numeric(param.ranges[10,3]) 

cost.trn.int <- (sampled.values[,11] * (as.numeric(param.ranges[11,4]) - as.numeric(param.ranges[11,3]))) + as.numeric(param.ranges[11,3])

cost.cme.int <- (sampled.values[,12] * (as.numeric(param.ranges[12,4]) - as.numeric(param.ranges[12,3]))) + as.numeric(param.ranges[12,3]) 

cost.hss.int <- (sampled.values[,13] * (as.numeric(param.ranges[13,4]) - as.numeric(param.ranges[13,3]))) + as.numeric(param.ranges[13,3])

cost.misc.int <- (sampled.values[,14] * (as.numeric(param.ranges[14,4]) - as.numeric(param.ranges[14,3]))) + as.numeric(param.ranges[14,3])

cost.fee.int <- (sampled.values[,15] * (as.numeric(param.ranges[15,4]) - as.numeric(param.ranges[15,3]))) + as.numeric(param.ranges[15,3])

cost.lab.int <- (sampled.values[,16] * (as.numeric(param.ranges[16,4]) - as.numeric(param.ranges[16,3]))) + as.numeric(param.ranges[16,3])

cost.med.int <- (sampled.values[,17] * (as.numeric(param.ranges[17,4]) - as.numeric(param.ranges[17,3]))) + as.numeric(param.ranges[17,3])

cost.trv.int <- (sampled.values[,18] * (as.numeric(param.ranges[18,4]) - as.numeric(param.ranges[18,3]))) + as.numeric(param.ranges[18,3])

cost.food.int <- (sampled.values[,19] * (as.numeric(param.ranges[19,4]) - as.numeric(param.ranges[19,3]))) + as.numeric(param.ranges[19,3])

cost.chc.int <- (sampled.values[,20] * (as.numeric(param.ranges[20,4]) - as.numeric(param.ranges[20,3]))) + as.numeric(param.ranges[20,3])

cost.mw.int <- (sampled.values[,21] * (as.numeric(param.ranges[21,4]) - as.numeric(param.ranges[21,3]))) + as.numeric(param.ranges[21,3])

cost.oth.int <- (sampled.values[,22] * (as.numeric(param.ranges[22,4]) - as.numeric(param.ranges[22,3]))) + as.numeric(param.ranges[22,3])

cost.test.con <- (sampled.values[,23] * (as.numeric(param.ranges[23,4]) - as.numeric(param.ranges[23,3]))) + as.numeric(param.ranges[23,3])

cost.cons.con <- (sampled.values[,24] * (as.numeric(param.ranges[24,4]) - as.numeric(param.ranges[24,3]))) + as.numeric(param.ranges[24,3])

cost.eqp.con <- (sampled.values[,25] * (as.numeric(param.ranges[25,4]) - as.numeric(param.ranges[25,3]))) + as.numeric(param.ranges[25,3])

cost.war.con <- (sampled.values[,26] * (as.numeric(param.ranges[26,4]) - as.numeric(param.ranges[26,3]))) + as.numeric(param.ranges[26,3])

cost.trn.con <- (sampled.values[,27] * (as.numeric(param.ranges[27,4]) - as.numeric(param.ranges[27,3]))) + as.numeric(param.ranges[27,3])

cost.cme.con <- (sampled.values[,28] * (as.numeric(param.ranges[28,4]) - as.numeric(param.ranges[28,3]))) + as.numeric(param.ranges[28,3])

cost.hss.con <- (sampled.values[,29] * (as.numeric(param.ranges[29,4]) - as.numeric(param.ranges[29,3]))) + as.numeric(param.ranges[29,3])

cost.misc.con <- (sampled.values[,30] * (as.numeric(param.ranges[30,4]) - as.numeric(param.ranges[30,3]))) + as.numeric(param.ranges[30,3])

cost.fee.con <- (sampled.values[,31] * (as.numeric(param.ranges[31,4]) - as.numeric(param.ranges[31,3]))) + as.numeric(param.ranges[31,3])

cost.lab.con <- (sampled.values[,32] * (as.numeric(param.ranges[32,4]) - as.numeric(param.ranges[32,3]))) + as.numeric(param.ranges[32,3])

cost.med.con <- (sampled.values[,33] * (as.numeric(param.ranges[33,4]) - as.numeric(param.ranges[33,3]))) + as.numeric(param.ranges[33,3])

cost.trv.con <- (sampled.values[,34] * (as.numeric(param.ranges[34,4]) - as.numeric(param.ranges[34,3]))) + as.numeric(param.ranges[34,3])

cost.food.con <- (sampled.values[,35] * (as.numeric(param.ranges[35,4]) - as.numeric(param.ranges[35,3]))) + as.numeric(param.ranges[35,3])

cost.chc.con <- (sampled.values[,36] * (as.numeric(param.ranges[36,4]) - as.numeric(param.ranges[36,3]))) + as.numeric(param.ranges[36,3])

cost.mw.con <- (sampled.values[,37] * (as.numeric(param.ranges[37,4]) - as.numeric(param.ranges[37,3]))) + as.numeric(param.ranges[37,3])

cost.oth.con <- (sampled.values[,38] * (as.numeric(param.ranges[38,4]) - as.numeric(param.ranges[38,3]))) + as.numeric(param.ranges[38,3])

sampled.values.true <- cbind( 
             num.test.int,
             num.test.con,
             ratio.oc.int,
             ratio.oc.con,
             ratio.ltc.int,
             ratio.ltc.con,
             cost.test.int,
             cost.cons.int,
             cost.eqp.int,
             cost.war.int,
             cost.trn.int,
             cost.cme.int,
             cost.hss.int,
             cost.misc.int,
             cost.fee.int,
             cost.lab.int,
             cost.med.int,
             cost.trv.int,
             cost.food.int,
             cost.chc.int,
             cost.mw.int,
             cost.oth.int,
             cost.test.con,
             cost.cons.con,
             cost.eqp.con,
             cost.war.con,
             cost.trn.con,
             cost.cme.con,
             cost.hss.con,
             cost.misc.con,
             cost.fee.con,
             cost.lab.con,
             cost.med.con,
             cost.trv.con,
             cost.food.con,
             cost.chc.con,
             cost.mw.con,
             cost.oth.con
            
)

```

```{R Run the Simulations}
#NO CHANGES
#Perform your simulations using a combination of apply() and do.call()
#apply() will iteratively perform the same function to each row and/or column of a matrix argument
#The matrix of sampled input values will serve as our matrix argument X
#We will set MARGIN=1 to indicate that we want to iterate over the rows (not columns) of the matrix
#We will create a custom function to apply over each row (r)
#The key of the custom function is do.call() 
#do.call() calls a function of your choice and passes user-defined arguments to it
#we will use it to call our previously-defined function treatment.sim()
#We will supply it our row of sampled input values as user-defined arguments
#arguments for do.call() must be in the form of a list: as.list(r)
#apply() returns the outputs of each iteration as a column of a matrix
#for ease of use, we will transpose - t() - the matrix so that each iteration will be returned as a row

sim.out<-t(apply(X=sampled.values.true,MARGIN=1, FUN=function(r) do.call(what=treatment.sim, args=as.list(r)) ))
#for each row of sampled.values, run function r which is our treatment.sim formula.
sim.out.df <- as.data.frame(sim.out)



#Becase treatment.sim() returns a vector of 4 results ("Scenario1.Cure","Scenario1.Cost","Scenario2.Cure","Scenario2.Cost")
#sim.out contains 4 columns, each corresponding to one of the outputs of treatment.sim()
#The first row of sim.out corresponds to the results of the simulation created by the first row of sampled input values in sampled.value
```

View(sim.out.df)
write.csv(sim.out.df, "Moz_sim.csv")

``` {r ICER values}
sim.out.df <- sim.out.df
ICER<-matrix(ncol=18, nrow=nrow(sim.out.df))
colnames(ICER)<-c("Overall cost intervention","Overall cost control","Incremental cost", "Total outcomes intervention", "Total outcomes control", "Incremental effectiveness","ICER","Per outcome cost intervention", "Per outcome cost control", "Number of tests intervention", "Number of tests control", "Cost per test intervention", "Cost per test control", "Total diagnosis intervention", "Total diagnosis control", "Cost per diagnosis intervention", "Cost per diagnosis control", "Secondary ICER")

ICER[,1]<- sim.out.df[,30] 

ICER[,2]<- sim.out.df[,50] 

ICER[,3] <- ICER[,1]-ICER[,2]

ICER[,4] <- sim.out.df[,7]

ICER[,5] <- sim.out.df[,8]

ICER[,6] <- ICER[,4]-ICER[,5]

ICER[,7] <- ICER[,3]/ICER[,6]

ICER[,8] <- ICER[,1]/ICER[,4]

ICER[,9] <- ICER[,2]/ICER[,5]

ICER[,10] <- sim.out.df[,1]

ICER[,11] <- sim.out.df [,2]

ICER[,12] <- ICER[,1]/ICER[,10]

ICER[,13] = ICER[,2]/ICER[,11]

ICER[,14] = sim.out.df[,9]

ICER [,15] =sim.out.df[,10]

ICER[,16] = ICER [,1]/ICER[,14]

ICER[,17] = ICER[,2]/ICER[,15]

ICER [,18] = ICER[,3]/(ICER[,14]-ICER[,15])
ICER.df <- data.frame(ICER)

#total cost intervention
#quantile(ICER.df[,7], 0.500)
#quantile(ICER.df[,7],0.025)
#quantile(ICER.df[,7],0.975)

# Create a vector of percentiles to calculate
percentiles <- c(0.025, 0.5, 0.975)

# Create an empty data frame to store the results
percentile_results <- data.frame()

# Iterate through each column in ICER.df and calculate percentiles
for (col_name in colnames(ICER.df)) {
  column_percentiles <- quantile(ICER.df[[col_name]], percentiles)
  
  # Create a new data frame to store the percentiles for the current column
  column_results <- data.frame(
    Column = col_name,
    Percentile_2.5 = column_percentiles[1],
    Percentile_50 = column_percentiles[2],
    Percentile_97.5 = column_percentiles[3]
  )
  
  # Add the results to the overall data frame
  percentile_results <- rbind(percentile_results, column_results)
}


##################
ICER_scenarios <- read.csv("ICER_scenarios.csv") #scenario 1 is moz base, then moz three tests, then tan base, then tan three tests or 

library(ggplot2)
library(reshape2)
library(dplyr)

# Assuming ICER_scenarios data frame is loaded with columns ICER_1, ICER_2, ICER_3, ICER_4

# Generate probabilities across a range of thresholds
thresholds <- seq(0, 1000, by = 50)
probabilities <- sapply(thresholds, function(threshold) {
  sapply(1:4, function(i) {
    mean(ICER_scenarios[[paste0("ICER_", i)]] <= threshold)
  })
})
probabilities <- t(probabilities)

# Create a dataframe for plotting
ceac_data <- data.frame(thresholds, probabilities)
ceac_data <- melt(ceac_data, id.vars = "thresholds", variable.name = "Scenario", value.name = "Probability")
ceac_data$Scenario <- factor(gsub("X", "", ceac_data$Scenario),
                             levels = c("1", "2", "3", "4"),
                             labels = c("Mozambique observed volume", "Mozambique 3 tests per day",
                                        "Tanzania observed volume", "Tanzania 3 tests per day"))

# Define specific thresholds to annotate
specific_thresholds <- c(250, 500, 750)

# Interpolate probabilities at specific thresholds for each scenario
annotated_data <- lapply(unique(ceac_data$Scenario), function(scenario) {
  scenario_data <- ceac_data %>% filter(Scenario == scenario)
  data.frame(Threshold = specific_thresholds,
             Probability = approx(scenario_data$thresholds, scenario_data$Probability, specific_thresholds)$y,
             Scenario = scenario)
}) %>% bind_rows()

# Filter out annotations for "Mozambique 3 tests per day"
annotated_data <- annotated_data %>% filter(Scenario != "Mozambique 3 tests per day")

# Create the plot with basic lines and vertical thresholds
p <- ggplot(ceac_data, aes(x = thresholds, y = Probability, color = Scenario, group = Scenario)) +
  geom_line(size = 1) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "black") +
  labs(x = "Willingness to Pay per Seven-Day TB Treatment Initiation (2022 US dollars)", 
       y = "Probability of Cost-Effectiveness",
       title = "Cost-Effectiveness Acceptability Curve (CEAC) for Different ICER Scenarios") +
  scale_x_continuous(breaks = seq(0, 1000, by = 100)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.1)) +
  theme_minimal() +
  xlim(0, 1000) +
  ylim(0, 1) +
  theme(legend.position = "top") +
  geom_vline(xintercept = specific_thresholds, color = "black") +
  geom_text(data = annotated_data, aes(x = Threshold, y = Probability - 0.025, label = round(Probability, 2)),  # Adjust labels to be closer to the line
            color = "black", size = 3.5, vjust = 1)  # Ensure vertical justification is set to align text above the coordinate

# Print the plot
print(p)

```
View(ICER.df)
View(percentile_results)
write.csv(percentile_results,"lamdapointseven_results_moz.csv")
#write.csv(ICER.df, "Moz_lamb3_ICER.csv")



```{r Calculate our beta distribution values}
#First calculate the Y value (mode) based on a desired peak/PE, X
yvalue <- function(x, min, max) {
  y <- ((x-min)/(max-min))
  return(y)
}
#Where y = mode of the distribution

betavalue <- function(a, y){
  beta <- ((a - 1)/y) - a + 2
  return(beta)
}
```